### 2022-10-30 CV2/general.tex
new papers

\section{Research Interests}
%Optimization Algorithms, Distributed Optimization, Machine Learning
\begin{tabular}{cl}
	\qquad\qquad&  Optimization Algorithms\\
	&  Distributed Optimization\\
	&  Machine Learning
\end{tabular}

@@

\begin{tabular}{rl}
	\textsc{Programming} & C/C++, Python; \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia\\
	\textsc{Computer} & macOS, LaTeX, Git\\
	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
\end{tabular}

>>>>

\section{Research Interests}
%Optimization Algorithms, Distributed Optimization, Machine Learning
\begin{tabular}{cl}
	\qquad\qquad&  Optimization Algorithms\\
	&  Distributed Optimization\\
	& Federated Learning\\
	&  Machine Learning
\end{tabular}

@@

\begin{tabular}{rl}
	\textsc{Programming} & C/C++, Python, Algorithms and Data Structures\\& \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia\\
	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
	\textsc{Computer} & macOS, LaTeX, Git\\
\end{tabular}

### 2022-10-30 CV2/papers.tex
new papers

@@

@@

@@

\item \textbf{Stochastic Distributed Learning with Gradient Quantization and Variance Reduction} (\href{https://samuelhorvath.github.io}{\color{linkcolour}Samuel Horvath}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://sstich.ch}{\color{linkcolour}Sebastian U. Stich}), \href{https://www.tandfonline.com/doi/abs/10.1080/10556788.2022.2117355}{\em \color{black}Optimization Methods and Software}

@@

@@

\item \textbf{Towards Accelerated Rates for Distributed Optimization over Time-varying Networks} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{}{\color{linkcolour}Vladislav Lukoshkin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://shulgin-egor.github.io}{\color{linkcolour}Egor Shulgin}), \href{https://arxiv.org/abs/2009.11069}{\em \color{black}arXiv preprint (September 2020)}

>>>>

\item \textbf{Accelerated Variance-Reduced Methods for Saddle-Point Problems} (\href{https://scholar.google.com/citations?user=9Dapoy8AAAAJ}{\color{linkcolour}Ekaterina Borodich}, \href{}{\color{linkcolour}Vladislav Tominin}, \href{}{\color{linkcolour}Yaroslav Tominin}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{http://wias-berlin.de/people/dvureche/}{\color{linkcolour}Pavel Dvurechensky}), \href{https://www.sciencedirect.com/science/article/pii/S2192440622000247}{\em \color{black}EURO Journal on Computational Optimization}

@@

\item \textbf{Accelerated Methods for Saddle-Point Problem} (\href{https://scholar.google.com/citations?user=dJgWojUAAAAJ}{\color{linkcolour}Mohammad Alkousa}, \href{https://scholar.google.com/citations?user=5ILnTRsAAAAJ}{\color{linkcolour}Darina Dvinskikh}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://www.researchgate.net/profile/Fedor_Stonyakin}{\color{linkcolour}Fedor Stonyakin}), \href{https://link.springer.com/article/10.1134/S0965542520110020}{\em \color{black}Computational Mathematics and Mathematical Physics}

@@

\item \textbf{Towards Accelerated Rates for Distributed Optimization over Time-varying Networks} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{}{\color{linkcolour}Vladislav Lukoshkin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://shulgin-egor.github.io}{\color{linkcolour}Egor Shulgin}), \href{https://link.springer.com/chapter/10.1007/978-3-030-91059-4_19}{\em \color{black}OPTIMA 2021}

@@

\item \textbf{Stochastic Distributed Learning with Gradient Quantization and Double Variance Reduction} (\href{https://samuelhorvath.github.io}{\color{linkcolour}Samuel Horvath}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://sstich.ch}{\color{linkcolour}Sebastian U. Stich}), \href{https://www.tandfonline.com/doi/abs/10.1080/10556788.2022.2117355}{\em \color{black}Optimization Methods and Software}

@@

\item \textbf{Decentralized Optimization over Time-varying Graphs: a Survey} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{}{\color{linkcolour}Aleksander Beznosikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://arxiv.org/abs/2210.09719}{\em \color{black}arXiv preprint (October 2022)}
\item \textbf{Smooth Monotone Stochastic Variational Inequalities and Saddle Point Problems - Survey} (\href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://sites.google.com/site/lab7polyak/}{\color{linkcolour}Boris Polyak}, \href{https://eduardgorbunov.github.io}{\color{linkcolour}Eduard Gorbunov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2208.13592}{\em \color{black}arXiv preprint (August 2022)}

@@
